---
title: "Aides Drug"
author: "Karen Hernandez"
date: "October 5, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
women<-filter(triUmp,gender=="F")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the females, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment,data=women)
barchartGC(~infected + treatment,data=women, type="percent")
```

As far as the chart goes we can see that the drug is working backwards. It does not looke like is working at all. Giving the choice of the drug or placebo to prevent aids, I would choose the placebo. It looks like the placebo works better than the drug to prevent aids. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment, data=women)
rowPerc(table1)
colPerc(table1)
```

This drug is not working correctly. If anything it is working backwards.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

If the null hypothesis was in compliant the way it should of come out is 172 people should of taken the drug and 184 should of taken the placebo, if it was exactly confirming the null hypothesis. But it did not come out that way. The chances of coming out this way that the null hypothesis was true is .0001, which is very low chances.The odds of getting the aids if you take the drug is 1 1/2 to 1 1/2 times more chances of getting aids if you take this drug than you did if you took the placebo. This is making the chances bigger and higher.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We can see the relationship between taking the drug or placebo to prevent aids. There is a difference if you take the drug, than you will get more chances of getting aids. The relationship between taking the drug and getting aids is that taking the drug seems to not work so we reject the null hypothesis that states there is no relationship and concludes that the relationship is negative. There is a relationship and its backwards than what we want. This drug will fail because it is working in the wrong direction and the relationship is working backwards. Between taking the drug or taking the placebo, the drug will increase the chances of getting aids.
